Elite individuals, insitutions, and economic growth accounting

### 2024-04-07 presentation/main.tex
add pre imputation stats

\begin{frame}{Summary Statistics}
    \begin{table}
        \caption{Summary Statistics}
        \resizebox{\linewidth}{!} {
            \begin{tabular}{lrrrrr}
            & Count & Mean & Std & Min & Max \\
            \\[-1.8ex]\hline
            \hline \\[-1.8ex]
            GDP per capita & 441.00 & 28463.99 & 25255.10 & 543.11 & 149461.79 \\
            GDP per capita growth (bps) & 440.00 & 169.06 & 452.68 & -2292.68 & 3303.05 \\
            Primary Completion & 441.00 & 90.00 & 10.25 & 51.35 & 101.95 \\
            Lower Sec. Completion & 441.00 & 77.89 & 17.14 & 29.21 & 101.97 \\
            Upper Sec. Completion & 441.00 & 62.20 & 18.48 & 18.44 & 97.40 \\
            Population & 441.00 & 35318600.19 & 59445620.16 & 34000.00 & 333287557.00 \\
            ARWU per million pop. ranked & 441.00 & 0.26 & 0.33 & 0.00 & 1.54 \\
            IMO score per log pop. & 441.00 & 4.72 & 3.49 & 0.00 & 11.79 \\
            PISA math in global 1\% & 441.00 & 0.94 & 1.46 & 0.00 & 14.64 \\
            PISA math & 441.00 & 461.93 & 56.23 & 315.96 & 574.66 \\
            \end{tabular}
        }
    \end{table}
\end{frame}

>>>>

\begin{frame}{Summary Statistics}
    \begin{table}
        \caption{Summary Statistics}
        \resizebox{\linewidth}{!} {
            \begin{tabular}{lrrrrr}
                & Count & Mean & Std & Min & Max \\
                \\[-1.8ex]\hline
                \hline \\[-1.8ex]
               GDP per capita & 441.00 & 28463.99 & 25255.10 & 543.11 & 149461.79 \\
               GDP per capita growth (bps) & 440.00 & 169.06 & 452.68 & -2292.68 & 3303.05 \\
               EIU Democracy Index & 441.00 & 7.25 & 1.77 & 1.93 & 9.93 \\
               Primary Completion & 441.00 & 90.00 & 10.25 & 51.35 & 101.95 \\
               Lower Sec. Completion & 441.00 & 77.89 & 17.14 & 29.21 & 101.97 \\
               Upper Sec. Completion & 441.00 & 62.20 & 18.48 & 18.44 & 97.40 \\
               Population & 441.00 & 35318600.19 & 59445620.16 & 34000.00 & 333287557.00 \\
               ARWU per million pop ranked & 441.00 & 0.26 & 0.33 & 0.00 & 1.54 \\
               IMO score per log pop & 441.00 & 4.72 & 3.49 & 0.00 & 11.79 \\
               PISA math in global 1\% & 441.00 & 0.94 & 1.46 & 0.00 & 14.64 \\
               PISA math & 441.00 & 461.93 & 56.23 & 315.96 & 574.66 \\
               \end{tabular}
        }
    \end{table}
    \begin{table}
        \tiny
        \caption{Pre-imputation Statistics}
        \begin{tabular}{lrrrrr}
         & Count & Mean & Std & Min & Max \\
         \\[-1.8ex]\hline
         \hline \\[-1.8ex]
        EIU Democracy Index & 323.00 & 7.09 & 1.78 & 1.93 & 9.93 \\
        Primary Completion & 157.00 & 90.29 & 10.31 & 51.35 & 100.00 \\
        Lower Sec. Completion & 179.00 & 76.63 & 20.03 & 29.21 & 99.98 \\
        Upper Sec. Completion & 198.00 & 62.32 & 20.58 & 18.44 & 97.40 \\
        \end{tabular}
        \end{table}
\end{frame}
